\documentclass[report.tex]{subfiles}
\begin{document}
\pagebreak \section{Introduction}
As modern, high frequency devices continue to raise the bar of what is technically possible, it is important to understand the basic principles by which they operate, and the tools used to develop them. 

This report does not only investigates the basic theory behind microstrips, transmission lines, propagation delays, impedance matching and Radio Frequency (RF) filters, but also show how Agilent Advanced Design System (ADS) can be used to calculate and measure different entities related to RF circuits, as well as developing and testing RF applications.

The different topics in this report are
\begin{itemize}
\item Simulation with Advanced Design System
\item Design of Matching Networks using ADS
\item RF Filter Design using ADS
\end{itemize}
The above topics are naturally divided in three chapters.

Each chapter has a short theoretical introduction which contains necessary background theory needed for that particular chapter. All the theory, except the theory that the authors of this report have misunderstood, can be found in the literature given in section \ref{subsec:References}.
After the theoretical background, a methodology section describes the ``how" of the chapter.
The methodology is followed by the results of the methods described.
The last section in each chapter discusses the obtained results.

To conclude this report, there is a conclusion chapter at the very end.

\subsection*{References}\label{subsec:References}
% \setcounter{secnumdepth}{1}
\begin{table}[H]
	\begin{tabular}{l l}
		[1] & R. Ludwig and G. Bogdanow, \\
		& \textit{RF Circuit Design - Theory and Applications}, 2 ed. \\
		& New Jersy: Pearson, 2009.
	\end{tabular}
\end{table}
\end{document}
